---
title       : The Amazing Graph
subtitle    : An answer to one of the world's greatest questions
author      : CesarTC
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Motivation

* If you have ever started to study statistics, you are probably familiar with some probability distributions.

* I could bet I know exactly the image that comes to your mind when I mention a **Normal Distribution**.


* That's because probability distributions associated with variables and events have very famous graphic representations.


* But life isn't about single variables, is it?

---

## Here's a very familiar plot

```{r, echo=FALSE}
set.seed(1234)
x <- seq(-4, 4, by = .04)
y <- dnorm(x, mean = 0, sd = 1)

plot(x, y, type = 'l', main = 'Normal Distribution Density Function')
```

---

## Here's another very familiar plot

```{r, echo=FALSE}
x <- seq(0, 20, by = .05)
y <- dchisq(x, df = 4)

plot(x, y, type = 'l', main = 'Chi-Squared Distribution Density Function')
```

---

## The Pitch

* Do you know what the interaction of two variables with those famous distributions would look like?

* Did you ever wonder how that interaction would change with different sets of means, standard deviations and degrees of freedom?

* Than here's the app for you!

* https://cesartc.shinyapps.io/DistributionsPlot/
